%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt, margin]{res}
 % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{hyperref}
\usepackage{setspace}
\hypersetup{colorlinks=true, linkcolor=blue, filecolor=magenta, urlcolor=cyan}
\usepackage{endnotes}
\usepackage{comment}
\let\footnote=\endnote
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\topmargin=-0.6in
\oddsidemargin -.3in
\evensidemargin -.5in
\setlength{\textwidth}{5.8in} % Text width of the document
\setlength{\textheight}{760 pt}
\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf \href{http://www.its.caltech.edu/~rkorol/index.html}{Roman Korol}} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{132 Noyes building, 1200 E. California Blvd} % Your address
\moveleft.5\hoffset\centerline{MC 127-72, Pasadena, CA, USA, 91125}
\moveleft.5\hoffset\centerline{+1 (626) 219-3728, \href{mailto:roman@caltech.edu}{roman@caltech.edu},}
\moveleft.5\hoffset\centerline{\href{https://ca.linkedin.com/in/roman-korol-a08656a8}{LinkedIn}, \href{https://scholar.google.ca/citations?user=YAAMduoAAAAJ&hl=en}{Google Scholar}, \href{https://www.researchgate.net/profile/Roman_Korol}{ResearchGate}}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
 
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{CURRENT OCCUPATION}

{\sl PhD candidate} \hfill start date: Fall 2018; passed candidacy February 2020\\
California Institute of technology, California, USA\\
Specialization: Theoretical Chemistry, Advisor: \href{https://millergroup.caltech.edu/Miller_Group/people/}{Thomas F. Miller III}\\

\section{EDUCATION}

{\sl Honors Bachelor of Science,} \hfill CGPA: 3.98/4.0 \hfill June 2018 \\
Faculty of Arts and Sciences, University of Toronto St. Michael's College, Canada \\
Specialization: Chemistry, Thesis: Dynamics of Protein Folding, Supervisor: Jeremy Schofield\\

 
{\sl Honors High School Diploma,}\hfill 99\% average \hfill  May 2014\\
M. Kravchuk Gymnasium 21, Lutsk, Ukraine\\
Specialization: Life sciences\\
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{RESEARCH EXPERIENCE}

{\sl Chemical Physics Theory Group, \href{http://www.chem.utoronto.ca/~dsegal/index.html}{Prof. D. Segal}} \hfill Summers 2016-2018 \\
Modelling DNA molecular junctions with Landauer-B\"uttiker probes

{\sl Chemical Physics Theory Group, \href{http://www.chem.utoronto.ca/~jmschofi/}{Prof. J. Schofield}} \hfill Fall 2017 -- Spring 2018 \\
Senior thesis project, University of Toronto:\\
Improving Fokker-Plank-based models of Protein folding dynamics
 
{\sl Inorganic Synthetic Laboratory, \href{http://www.chem.utoronto.ca/staff/DSTEPHAN/index.htm}{University Prof. D. Stephan}} \hfill Winter -- Spring 2016 \\
Synthesis of Boron-containing air-stable FLP radicals

{\sl Organic Materials Laboratory, \href{https://www.weizmann.ac.il/Organic_Chemistry/Rybtchinski/}{Prof. B. Rybtchinski}} \hfill Summer 2015 \\
\href{https://www.weizmann.ac.il/feinberg/admissions/kupcinet-getz-international-Summer-school/about-program-0}{Kupcinet-Getz Summer School}, Weizmann Institute of Science, Rehovot, Israel\\
Self-assembly, fluorescence and non-linear properties of organic PDI nanocrystals

{\sl Inorganic Synthetic Laboratory, \href{http://www.utm.utoronto.ca/fekl/}{Associate Prof. U. Fekl}} \hfill Fall 2014 -- Spring 2015 \\
\textit{Topic:} Functionalization of di- and trihalogenated adamantanes

{\sl Inorganic materials Laboratory, Dr. O. Yanchuk} \hfill Summer 2013 -- Spring 2014 \\
Junior Academy of Sciences \& Eastern European National University, Lutsk, Ukraine\\

\begin{comment}
\section{PUBLICATIONS}
\begin{itemize}
	\item \textbf{Korol, R.}; Bou-Rabee,  N.; Miller III, T.F. Cayley modification for strongly stable path-integral and ring-polymer molecular dynamics. \textit{J. Chem. Phys.} \textbf{2019}, 151 (12), 124103. \href{https://aip.scitation.org/doi/10.1063/1.5120282}{10.1063/1.5120282}

	\item \textbf{Korol, R.}; Segal, D. Machine Learning Prediction of DNA Charge Transport. \textit{J. Phys. Chem. B} \textbf{2019}, 123 (13), pp 2801 –- 2811. \href{https://pubs.acs.org/doi/full/10.1021/acs.jpcb.8b12557}{10.1021/acs.jpcb.8b12557}

	\item \textbf{Korol, R.}; Segal D. From Exhaustive Simulations to Key Principles in DNA Nanoelectronics. \textit{J. Phys. Chem. C} \textbf{2018}, 122 (8), pp 4206 –- 4216. \href{https://pubs.acs.org/doi/full/10.1021/acs.jpcc.7b12744}{10.1021/acs.jpcc.7b12744}
	
	\item \textbf{Korol, R.}; Kilgour,  M.; Segal, D. ProbeZT: Simulation of transport coefficients of molecular electronic junctions under environmental effects using B\"uttiker’s probes. \textit{Comput. Phys. Comm.} \textbf{2018}, 224, 396–404. \href{https://doi.org/10.1016/j.cpc.2017.10.005}{10.1016/j.cpc.2017.10.005}
	
	\item \textbf{Korol, R.}; Kilgour,  M.; Segal, D. Thermopower Of Molecular Junctions: Tunneling To Hopping Crossover In DNA. \textit{J. Chem. Phys} \textbf{2016}, 145 (22), 224702. \href{http://aip.scitation.org/doi/10.1063/1.4971167}{10.1063/1.4971167}
	
	\item Longobardi, L.E.; Zatsepin, P.; \textbf{Korol, R.}; Liu, L.; Grimme, S.; Stephan D.W. Reactions Of Boron-Derived Radicals With Nucleophiles. \textit{J. Am. Chem. Soc.} \textbf{2016} 139 (1), pp 426–-435. \href{http://pubs.acs.org/doi/abs/10.1021%2Fjacs.6b11190}{10.1021/jacs.6b11190} 
		%	\item \textbf{Korol, R.}; Marchuk, V.; Urubkov I.V.; Yanchuk O.M. Controlling the Size and Morphology of ZnO Nanorods in Two-electrode Synthesis Using Auxiliary Stabilizers
		%	(manuscript in preparation) 			
	\end{itemize}
\newpage
\end{comment}
\section{PRESENTATIONS}
 \bigskip Contributed talks: 
 \begin{itemize}
 \item DNA Molecular Junctions:  Tunneling to Hopping Crossover -- Chemical Biophysics \href{www.chembiophys.ca}{Symposium}--2017 (U of Toronto)
 \item Probing mechanisms of charge transport in DNA with Landauer-B\"uttiker formalism -- \href{http://scp.uwaterloo.ca}{33\textsuperscript{rd} Symposium} on Chemical Physics--2017 (U of Waterloo)
 \end{itemize}
 Poster presentations: 
 \begin{itemize}
 \item Principles of Charge Transport in DNA: from extensive simulations to neural networkds -- Berkeley Statistical Mechanics  \href{http://berkeleystatmech.org/}{Meeting}--2019 (Berkeley)
 \item Principles of Charge Transport in DNA: from extensive simulations to neural networkds -- CECAM BioMolecular Electronics \href{https://www.cecam.org/workshop-0-1522.html}{Conference}--2018 (Universidad Autónoma de Madrid)
 \end{itemize}
\newpage
Conference awards:
\begin{itemize}
	\item 1\textsuperscript{st} prize at the 45th Southern Ontario Undergraduate Student Chemistry \href{http://www.souscc45.ca}{Conference}, Computational section (Toronto, 2017) %(\$80)
	\item 1\textsuperscript{st} poster prize in Physical/Theoretical/Computational Undergraduate section at the 100\textsuperscript{th} Canadian Chemistry \href{http://www.csc2017.ca/student-competitions-0}{Conference} (Toronto, 2017) %(\$150)
	\item  Undergraduate Poster Prize at the 28\textsuperscript{th} Canadian \href{http://catc.chem.ubc.ca/home/welcome}{Symposium} on Theoretical and Computational Chemistry (Windsor, 2018) %(\$500)
\end{itemize}


%----------------------------------------------------------------------------------------
\section{AWARDS \& HONORS} 
Research funding:
\begin{itemize}
	\item Fall 2018  -- G. Patricia “Pat” Beckman Graduate Fellowship %(\$56,440=\$22,440 in tuition + \$34,000 stipend)
	\item Summer 2018 -- University of Toronto {\href{http://www.research.utoronto.ca/research-funding-opportunities/2013-university-of-toronto-excellence-awards-utea/}{Excellence Award}} %(CAD\$6,000)
	\item Summer 2017 -- University of Toronto {\href{http://www.research.utoronto.ca/research-funding-opportunities/2013-university-of-toronto-excellence-awards-utea/}{Excellence Award}} %(CAD\$6,000)
	\item Summer 2017 -- \href{https://cqiqc.physics.utoronto.ca/programs/index.html}{Center for Quantum Information and Quantum Control} Undergraduate Summer Research Studentship %(CAD\$9,000)
	\item Summer 2016 -- University of Toronto \href{http://www.research.utoronto.ca/research-funding-opportunities/2013-university-of-toronto-excellence-awards-utea/}{Excellence Award} %(CAD\$6,000)
\end{itemize}
Academic:
\begin{itemize}
	\item November 2018 -- Ivan Szak Scholarship in Chemistry %Awarded to the graduate with the highest cumulative grade point average in the Specialist program in Chemistry(CAD\$200)
	\item June 2018 -- St. Michael's College Silver Medal %Awarded to graduating students with a CGPA of at least 3.70 in any area of study
	\item May 2018 -- St. Michael's College In-Course Scholarship %(CAD\$1500)
	\item January 2018 -- Canadian Society for Chemistry \href{http://www.cheminst.ca/awards/student-awards/csc-silver-medal} {Silver medal} %-- awarded to an outstanding student in the Specialist Program in Chemistry with an A average
	\item December 2017 -- Ivan Szak Prize in Chemistry %- awarded to the graduate with the highest cumulative GPA in the Specialist Program in Chemistry %(CAD\$300)
	\item November 2017 -- F. E. Beamish Scholarship in Chemistry %-- awarded to an outstanding student whose programme includes at least three 300 level or higher courses in Chemistry %(CAD\$1000)
	\item May 2017 -- John Melady Memorial Scholarship %(CAD\$50)
	\item April 2017 -- C. W. Burton In-Course Scholarship %(CAD\$1000)
	\item April 2017 -- The Sarah Cusick Gollop And William George Gollop Memorial Undergraduate Scholarship in Chemistry %(CAD\$700) - awarded to an outstanding student in a Specialist Program in Chemistry
	\item 2016-2017 -- Dean’s List Scholar at the Faculty of Arts and Science, University of Toronto
	\item 2014-2015 --  \href{https://www.utm.utoronto.ca/cps/honour-roll/2014-15}{Honour Roll} of the Department of Chemical and Physical Sciences, University of Toronto Mississauga
	\item September 2014 -- Erindale Admission Scholarship %(CAD\$2000)
	\item 2013-2014 -- Scholarship of the President of Ukraine %(\$2000)
	\item May 2014 -- Student of the year in Lutsk and Volyn Region %(\$500)
	\item First Prize at Intel-Eco Ukraine 2014, the national stage of \href{https://student.societyforscience.org/intel-isef}{Intel ISEF}
	\item Gold medal at the International Ecology Project Olympiad-2013
	\item First and second prizes won in yearly National competitions in Ukraine: four times at the  Chemistry Olympiad, twice at the Ecology Olympiad, thrice at the Biology tournament
\end{itemize}
Others:
\begin{itemize}
	\item April 2018 -- Ukrainian Credit Union  Michael Rebryk Memorial  \href{http://ucu-building-community.blogspot.ca/2016/03/ucu-adds-new-scholarships-in-2016.html}{Scholarship}
	\item September 2017 -- Buduchnist Credit Union \href{http://www.buduchnist.com/scholarships}{Scholarship} %(CAD\$1500)
	\item January 2017 -- Michael Both Award "For Outstanding Commitment to Dance \& Contribution to the Desna Ukrainian Dance Company" %(CAD\$500)
\end{itemize}


%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------
\section{WORKSHOPS}
{\sl \href{http://vaikuntanathan-group.uchicago.edu/TSRC/telluride2019.html}{Telluride School on Theoretical Chemistry} at \href{https://www.telluridescience.org/schools/tellurideschoolontheoreticalchemistry}{TSRC}} \hfill Summer 2019 \\
Statistical Mechanics (\href{https://chemistry.uchicago.edu/faculty/suri-vaikuntanathan}{Suri Vaikuntanathan}), Electronic Structure (\href{https://chem.columbia.edu/people/faculty/timothy-berkelbach/}{Tim Berkelbach}), Quantum Dynamics (\href{http://www.sas.rochester.edu/chm/people/faculty/franco-ignacio/index.html}{Ignacio Franco}), Biophysics (\href{https://bmb.natsci.msu.edu/faculty/michael-feig/}{Michael Feig})

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{SKILLS} 

{\sl Languages \& Software:} Python, Matlab, Mathematica, Bash, C++, Git, Fortran\\
{\sl Experimental:} Synthesis in glove box, basic purification (HPLC, prep. TLC etc.), analysis (NMR, FTIR, Raman, AAS, AES), fluorescence and absorbance studies, SEM and TEM.


\section{WORK \\ EXPERIENCE} 

\begin{itemize}
\item Ukrainian transcriber and Research assistant working on the Heritage language variation and change (studying Ukrainian) \href{http://projects.chass.utoronto.ca/ngn/HLVC/0_0_home.php}{project}, supervised by \href{http://individual.utoronto.ca/ngn/}{Dr. N. Nagy}\\ Department of Linguistics, University of Toronto 
\item Private High school and freshman Chemistry, Physics and Mathematics tutoring
\end{itemize}

\section{OTHER \\ ACTIVITIES} 

\begin{itemize}
	\item Spring 2020 - Running \href{https://causetutoring.org/online-extra-help-sessions-during-covid-19/}{online help sessions} for high school Math and Science students as part of the \href{https://causetutoring.org/}{CAUSE tutoring} nonprofit
	\item Summer 2019 - Organized and taught two week-long Science Summer schools "Knowledge hunt" for High School and Middle School students respectively in my hometown, \href{https://en.wikipedia.org/wiki/Lutsk}{Lutsk}, Ukraine
	\item Fall 2018 - continuing Ukrainian folk dancing with \href{https://kalyna.org/}{Chervona Kalyna} Los Angeles dance ensemble
	\item 2018-2019 Volonteer at the \href{https://www.caltechy.org/single-post/2019/05/01/Caltech-Y-Volunteers-Make-Science-Exciting-at-Elementary-School}{Pasadena LEARNs} program -- science demos at local Elementary schools
	\item Summer of 2018 Lecturer for the Canadian team training for the $50^{th}$ International Chemistry Olympiad, \href{https://50icho.eu}{IChO-2018} 
	\item 2015-2018 member of \textit{We Love UA -- Canada}, a volunteer organization promoting Ukrainian culture in Canada
	\item 2016-2018 Ukrainian folk dancing with \href{http://www.desna.ca}{Desna} Ukrainian Dance Company and \href{http://www.infoukes.com/vesnianka/}{Vesnianka} Ukrainian Dance Ensemble
	\item 2015-2018 Chemistry and Maths Tutor at the University of Toronto Peer Tutoring group 
	\item 2015-2016 Board member of the \href{http://csu.sa.utoronto.ca/exceutive-team-2015-2016/}{Chemistry Student Union} and Chemistry Connections (student Group)
	\item Summers of 2014-2016 Student coach at M. Kravchuk Gymnasium 21, Lutsk, Ukraine
\end{itemize}
Member of the:
\begin{itemize}
	\item American Chemical Society (since 2016)
	\item Canadian Society of Chemistry (2016-2018)
\end{itemize}

%----------------------------------------------------------------------------------------
\end{resume}

\end{document}